---
title: "Trait Covariation"
author: "Jon Nations"
date: "8/27/2020"
output: html_document
---
This markdown provides the code for the trait covariation analyses in Nations et al. `Locomotory mode transitions alter phenotypic evolution and lineage diversification in an ecologically rich clade of mammals`.

These are used in the third section of the methods entitled `Trait covariation and integration`

Read more about multivariate multilevel models in brms here: https://cran.r-project.org/web/packages/brms/vignettes/brms_multivariate.html

Set directory
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users....")
```
Packages
Written using:
brms 2.13.3
```{r}
library(brms)
library(tidyverse)
library(MCMCglmm)
library(phytools)
library(geiger)
```
## Load Data
Individual csv files for each locomotor mode model
Full file for complete correlation model
```{r}
tree <- read.tree("MCCtree.nwk")
A_dat <- read.csv("Data_Cor_Arboreal.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
C_dat <- read.csv("Data_Cor_General.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
T_dat <- read.csv("Data_Cor_Terrestrial.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
SA_dat <- read.csv("Data_Cor_Amphibious.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
dat <- read.csv("Data_Cor_All.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
A_dat$logmass <- as.numeric(scale(A_dat$logmass))
T_dat$logmass <- as.numeric(scale(T_dat$logmass))
C_dat$logmass <- as.numeric(scale(C_dat$logmass))
SA_dat$logmass <- as.numeric(scale(SA_dat$logmass))
dat$logmass <- as.numeric(scale(dat$logmass))
```

## Prepare Covariance Matrices
List of arboreal species
```{r}
treedat <- treedata(tree, A_dat, warnings = F)
atip <- treedat$phy$tip.label
Atree <- keep.tip(tree,tip=atip)
```
prepare tree for model
```{r}
inv.phylo <- MCMCglmm::inverseA(Atree, nodes = "TIPS", scale = TRUE)
AA <- solve(inv.phylo$Ainv)
rownames(AA) <- rownames(inv.phylo$Ainv)
```

list of general species
```{r}
treedat <- treedata(tree, C_dat, warnings = F)
ctip <- treedat$phy$tip.label
Ctree <- keep.tip(tree,tip=ctip)
```
prepare general tree
```{r}
inv.phylo <- MCMCglmm::inverseA(Ctree, nodes = "TIPS", scale = TRUE)
CA <- solve(inv.phylo$Ainv)
rownames(CA) <- rownames(inv.phylo$Ainv)
```

list of terrestrial species
```{r}
treedat <- treedata(tree, T_dat, warnings = F)
ttip <- treedat$phy$tip.label
Ttree <- keep.tip(tree,tip=ttip)
```
prepare terrestrial tree
```{r}
inv.phylo <- MCMCglmm::inverseA(Ttree, nodes = "TIPS", scale = TRUE)
TA <- solve(inv.phylo$Ainv)
rownames(TA) <- rownames(inv.phylo$Ainv)
```
list of amphibious species
```{r}
treedat <- treedata(tree, SA_dat, warnings = F)
satip <- treedat$phy$tip.label
SAtree <- keep.tip(tree,tip=satip)
```
prepare amphibious tree
```{r}
inv.phylo <- MCMCglmm::inverseA(SAtree, nodes = "TIPS", scale = TRUE)
SAA <- solve(inv.phylo$Ainv)
rownames(SAA) <- rownames(inv.phylo$Ainv)
```


list of all species
```{r}
treedat <- treedata(tree, dat, warnings = F)
alltip <- treedat$phy$tip.label
Alltree <- keep.tip(tree,tip=alltip)
```
prepare all species tree
```{r}
inv.phylo <- MCMCglmm::inverseA(Alltree, nodes = "TIPS", scale = TRUE)
All <- solve(inv.phylo$Ainv)
rownames(All) <- rownames(inv.phylo$Ainv)
```

# Models
## Arboreal Trait Covariance
The `mvbind()` binds the four response variables together. These models then estimate the correlation between each of the four response variables, conditioned on the phylogeny
```{r}
A_cor <- brm(mvbind(hb, tail_index, hf_hb, logmass) ~ 0 + (1|gr(phylo, cov = A)),
  data = A_dat,
  data2 = list(A = AA),
  family = student(link = "identity"),
  iter = 5000,
 prior = c(
  set_prior("gamma(2,0.5)", class = "nu"),
  set_prior("normal(0,1)", class = "sd", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", resp = "logmass"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "logmass"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "tailindex"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hfhb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "logmass")),
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  inits = "0",
  cores = 2#,
 #add file name here if you want to save rds
 #file = "Arboreal_Correlation"
)

```

```{r}
summary(A_cor)
```
```{r}
plot(A_cor, N=3, ask = F)
```

## General Trait Covariance
```{r}
C_cor <- brm(mvbind(hb, tail_index, hf_hb, logmass) ~ 0 +  (1|gr(phylo, cov = A)),
  data = C_dat,
  data2 = list(A = CA),
  family = student(link = "identity"),
  iter = 5000,
 prior = c(
  set_prior("gamma(2,0.5)", class = "nu"),
  set_prior("normal(0,1)", class = "sd", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", resp = "logmass"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "logmass"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "tailindex"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hfhb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "logmass")),
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  inits = "0",
  cores = 2#,
 #add file name here if you want to save rds
 #file = "Arboreal_Correlation"
)

```

```{r}
summary(C_cor)
```

```{r}
plot(C_cor, N=3, ask = F)
```

## Terrestrial Trait Covariance
```{r}
T_cor <- brm(mvbind(hb, tail_index, hf_hb, logmass) ~ 0 +  (1|gr(phylo, cov = A)),
  data = T_dat,
  data2 = list(A = TA),
  family = student(link = "identity"),
  iter = 5000,
 prior = c(
  set_prior("gamma(2,0.5)", class = "nu"),
  set_prior("normal(0,1)", class = "sd", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", resp = "logmass"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "logmass"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "tailindex"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hfhb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "logmass")),
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  inits = "0",
  cores = 2#,
 #add file name here if you want to save rds
 #file = "Arboreal_Correlation"
)

```

```{r}
summary(T_cor)
```

```{r}
plot(T_cor, N=3, ask = F)
```

## Amphibious Trait Covariance
```{r}
SA_cor <- brm(mvbind(hb, tail_index, hf_hb, logmass) ~ 0 +  (1|gr(phylo, cov = A)),
  data = SA_dat,
  data2 = list(A = SAA),
  family = student(link = "identity"),
  iter = 5000,
 prior = c(
  set_prior("gamma(2,0.5)", class = "nu"),
  set_prior("normal(0,1)", class = "sd", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", resp = "logmass"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "logmass"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "tailindex"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hfhb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "logmass")),
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  inits = "0",
  cores = 2#,
 #add file name here if you want to save rds
 #file = "Arboreal_Correlation"
)

```

```{r}
summary(SA_cor)
```

```{r}
plot(SA_cor, N=3, ask = F)
```

## All Trait Covariance

```{r}
All_cor <- brm(mvbind(hb, tail_index, hf_hb, logmass) ~ 0 +  (1|gr(phylo, cov = A)),
  data = dat,
  data2 = list(A = All),
  family = student(link = "identity"),
  iter = 5000,
 prior = c(
  set_prior("gamma(2,0.5)", class = "nu"),
  set_prior("normal(0,1)", class = "sd", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", resp = "logmass"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "tailindex"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "hfhb"),
  set_prior("normal(0,1)", class = "sd", group = "phylo", resp = "logmass"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "tailindex"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "hfhb"),
  set_prior("normal(0.2,0.5)", class = "sigma", resp = "logmass")),
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  inits = "0",
  cores = 2#,
 #add file name here if you want to save rds
 #file = "Arboreal_Correlation"
)

```

```{r}
summary(All_cor)
```

```{r}
plot(All_cor, N=3, ask = F)
```

