---
title: "Comparing Morphologies Between Locomotor Modes"
author: "Jon Nations"
date: "8/27/2020"
output: html_document
---

This markdown provides the code for estimating the phylogenetically corrected mean trait values for each locomotor mode, and the scripts to do calculate the differences/contrasts, from Nations et al. `Locomotory mode transitions alter phenotypic evolution and lineage diversification in an ecologically rich clade of mammals`.

Set directory
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/Dicrostonyx/Documents/Projects/AncSt/Manuscript/Evolution_Submission/GitHub")
```
Packages
Written using: brms 2.13.3
```{r}
library(brms)
library(tidyverse)
library(MCMCglmm)
library(phytools)
library(geiger)
```
## Load Data
Individual csv files for each locomotor mode model
Full file for complete correlation model
```{r}
trees <- read.tree("1000.nex")
trees <- sample(trees, size = 100)
trees <- lapply(trees, force.ultrametric)
dat <- read.csv("Scaled_Data.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
```

## Remove extra tips
```{r}
tree <- trees[[1]]
write.tree(tree, file = "one_tree.nwk")
dtt <- read.tree("one_tree.nwk")
```
geiger::treedata
```{r}
treedat <- treedata(dtt, dat, warnings = F)
tips <- treedat$phy$tip.label
tree_samp <-lapply(trees,keep.tip,tip=tips)
class(tree_samp)<-"multiPhylo"
```

##Covariance Matrix
Generate list of 100 covariance matrices
```{r}
inverse<-list()
As <- list()
for (i in 1:length(trees) ) {
  inverse[[i]] <- inverseA(trees[[i]], nodes = "TIPS", scale = TRUE)
  x <- solve(inverse[[i]]$Ainv)
  rownames(x) <- rownames(inverse[[i]]$Ainv)
  As[[i]] <- x
}
```

## Models
#### Warning: These take a Long Time to Run
Run model using one tree, then loop model over the 100 trees from the posterior distribution using `brms::update`
Then merge all the models together, and save the `.rds` file
#### Total Length
```{r}
total.fit <- brm(
  total ~ 0 + state_name + (1|gr(phylo, cov = A)),
  data = dat,
  data2 = list(A = As[[1]]),
  family = student(link = "identity"),
  iter = 5000,
  thin = 10,
  save_all_pars = TRUE,
 prior = c(
  set_prior("normal(0,1.5)", class = "b"),
  set_prior("normal(0,1.5)", class = "sd")),
  inits = "0",
  cores = parallel::detectCores()
)

total.fits <- vector("list", 100) 
for (i in seq_along(total.fits)) {
total.fits[[i]] <- update(total.fit,
                      data2 = list(A = As[[i]],
                      cores = parallel::detectCores())
)
}

```
#### Combine and Save Model
Then remove the large file
```{r}
total.fits_comb <- combine_models(total.fits[[i]], mlist = total.fits)
saveRDS(total.fits_comb, file = "/Users/.../......Rds", compress = F)
summary(total.fits_comb)
plot(total.fits_comb, N=3, ask = F)
```

#### Compile the Draws using Tidybayes
Remove the big model object
Then save an rds file with JUST the draws and not all the other stuff.
```{r}
total_draws <- gather_draws(total.fits_comb, b_state_nameA, b_state_nameC, b_state_nameT, b_state_nameSA) 
rm(total.fits_comb)
total_draws$.variable[total_draws$.variable == "b_state_nameA"] <- "Arboreal"
total_draws$.variable[total_draws$.variable == "b_state_nameC"] <- "General"
total_draws$.variable[total_draws$.variable == "b_state_nameT"] <- "Terrestrial"
total_draws$.variable[total_draws$.variable == "b_state_nameSA"] <- "Amphibious"
saveRDS(total_draws, file = "/Users/.../....../total.gathered.Rds")
```

#### Relative Tail Length
```{r}
tail.fit <- brm(
  tail_index ~ 0 + state_name + (1|gr(phylo, cov = A)),
  data = dat,
  data2 = list(A = As[[1]]),
  family = student(link = "identity"),
  iter = 5000,
  thin = 10,
  save_all_pars = TRUE,
 prior = c(
  set_prior("normal(0,1.5)", class = "b"),
  set_prior("normal(0,1.5)", class = "sd")),
  inits = "0",
  cores = parallel::detectCores()
)

tail.fits <- vector("list", 100) 
for (i in seq_along(tail.fits)) {
tail.fits[[i]] <- update(tail.fit,
                      data2 = list(A = As[[i]],
                      cores = parallel::detectCores())
)
}

```
#### Combine and Save Model
Then remove the large file
```{r}
tail.fits_comb <- combine_models(tail.fits[[i]], mlist = tail.fits)
saveRDS(tail.fits_comb, file = "/Users/.../......Rds", compress = F)
summary(tail.fits_comb)
plot(tail.fits_comb, N=3, ask = F)
```

#### Compile the Draws using Tidybayes
Remove the big model object
Then save an rds file with JUST the draws and not all the other stuff.
```{r}
tail_draws <- gather_draws(tail.fits_comb, b_state_nameA, b_state_nameC, b_state_nameT, b_state_nameSA) 
rm(tail.fits_comb)
tail_draws$.variable[tail_draws$.variable == "b_state_nameA"] <- "Arboreal"
tail_draws$.variable[tail_draws$.variable == "b_state_nameC"] <- "General"
tail_draws$.variable[tail_draws$.variable == "b_state_nameT"] <- "Terrestrial"
tail_draws$.variable[tail_draws$.variable == "b_state_nameSA"] <- "Amphibious"
saveRDS(tail_draws, file = "/Users/.../....../tail.gathered.Rds")
```


#### Relative Foot Size
```{r}
foot.fit <- brm(
  hf_hb ~ 0 + state_name + (1|gr(phylo, cov = A)),
  data = dat,
  data2 = list(A = As[[1]]),
  family = student(link = "identity"),
  iter = 5000,
  thin = 10,
  save_all_pars = TRUE,
 prior = c(
  set_prior("normal(0,1.5)", class = "b"),
  set_prior("normal(0,1.5)", class = "sd")),
  inits = "0",
  cores = parallel::detectCores()
)

foot.fits <- vector("list", 100) 
for (i in seq_along(foot.fits)) {
foot.fits[[i]] <- update(foot.fit,
                      data2 = list(A = As[[i]],
                      cores = parallel::detectCores())
)
}

```
#### Combine and Save Model
Then remove the large file
```{r}
foot.fits_comb <- combine_models(foot.fits[[i]], mlist = foot.fits)
saveRDS(foot.fits_comb, file = "/Users/.../......Rds", compress = F)
summary(foot.fits_comb)
plot(foot.fits_comb, N=3, ask = F)
```
#### Compile the Draws using Tidybayes
Remove the big model object
Then save an rds file with JUST the draws and not all the other stuff.
```{r}
foot_draws <- gather_draws(foot.fits_comb, b_state_nameA, b_state_nameC, b_state_nameT, b_state_nameSA) 
rm(foot.fits_comb)
foot_draws$.variable[foot_draws$.variable == "b_state_nameA"] <- "Arboreal"
foot_draws$.variable[foot_draws$.variable == "b_state_nameC"] <- "General"
foot_draws$.variable[foot_draws$.variable == "b_state_nameT"] <- "Terrestrial"
foot_draws$.variable[foot_draws$.variable == "b_state_nameSA"] <- "Amphibious"
saveRDS(foot_draws, file = "/Users/.../....../foot.gathered.Rds")
```

#### Mass
```{r}
mass.fit <- brm(
  logmass ~ 0 + state_name + (1|gr(phylo, cov = A)),
  data = dat,
  data2 = list(A = As[[1]]),
  family = student(link = "identity"),
  iter = 5000,
  thin = 10,
  save_all_pars = TRUE,
 prior = c(
  set_prior("normal(0,1.5)", class = "b"),
  set_prior("normal(0,1.5)", class = "sd")),
  inits = "0",
  cores = parallel::detectCores()
)

mass.fits <- vector("list", 100) 
for (i in seq_along(mass.fits)) {
mass.fits[[i]] <- update(mass.fit,
                      data2 = list(A = As[[i]],
                      cores = parallel::detectCores())
)
}

```
#### Combine and Save Model
Then remove the large file
```{r}
mass.fits_comb <- combine_models(mass.fits[[i]], mlist = mass.fits)
saveRDS(mass.fits_comb, file = "/Users/.../......Rds", compress = F)
summary(mass.fits_comb)
plot(mass.fits_comb, N=3, ask = F)
```

#### Compile the Draws using Tidybayes
Remove the big model object
Then save an rds file with JUST the draws and not all the other stuff.
```{r}
mass_draws <- gather_draws(mass.fits_comb, b_state_nameA, b_state_nameC, b_state_nameT, b_state_nameSA) 
rm(mass.fits_comb)
mass_draws$.variable[mass_draws$.variable == "b_state_nameA"] <- "Arboreal"
mass_draws$.variable[mass_draws$.variable == "b_state_nameC"] <- "General"
mass_draws$.variable[mass_draws$.variable == "b_state_nameT"] <- "Terrestrial"
mass_draws$.variable[mass_draws$.variable == "b_state_nameSA"] <- "Amphibious"
saveRDS(mass_draws, file = "/Users/.../....../mass.gathered.Rds")
```

# Plot Differences
#### Total

Fix names and plot
```{r}
total_plot <- total_draws %>%
  filter(row_number() %% 10 == 1) %>%
  compare_levels(.value, by = .variable)  %>%
  ungroup() %>%
  mutate(condition = reorder(.variable, .value)) %>%
  ggplot(aes(y = .variable, x = .value)) + 
  geom_halfeyeh() + 
  #stat_dotsh(quantiles = 150, dotsize = 1.2) +
  geom_vline(xintercept = c(0), linetype = "dashed") +
  scale_fill_manual(values = c("gray80")) + 
  labs(x = "Relative Total Differences\n",
       y = "",
       #title = "Total",
       center = T) +
  theme(plot.title = element_text(size=7)) + 
  theme(axis.title.y  = element_text(size = 4)) +
  theme_bw()

#output_file = "totalContrasts.pdf"
#ggsave(output_file, width = 9, height = 4.5)
```

#### Tail

```{r}
tail_plot <- tail_draws %>%
  filter(row_number() %% 10 == 1) %>%
  compare_levels(.value, by = .variable)  %>%
  ungroup() %>%
  mutate(condition = reorder(.variable, .value)) %>%
  ggplot(aes(y = .variable, x = .value)) + 
  geom_halfeyeh() + 
  #stat_dotsh(quantiles = 150, dotsize = 1.2) +
  geom_vline(xintercept = c(0), linetype = "dashed") +
  scale_fill_manual(values = c("gray80")) + 
  labs(x = "Relative Tail Differences\n",
       y = "",
       #title = "Tail",
       center = T) +
  theme(plot.title = element_text(size=7)) + 
  theme(axis.title.y  = element_text(size = 4)) +
  theme_bw()

#output_file = "tail_Contrasts.pdf"
#ggsave(output_file, width = 9, height = 4.5)
```

#### Foot

```{r}
foot_plot <- foot_draws %>%
  filter(row_number() %% 10 == 1) %>%
  compare_levels(.value, by = .variable)  %>%
  ungroup() %>%
  mutate(condition = reorder(.variable, .value)) %>%
  ggplot(aes(y = .variable, x = .value)) + 
  geom_halfeyeh() + 
  #stat_dotsh(quantiles = 150, dotsize = 1.2) +
  geom_vline(xintercept = c(0), linetype = "dashed") +
  scale_fill_manual(values = c("gray80")) + 
  labs(x = "Relative Hind Foot Differences\n",
       y = "",
       #title = "Hind Foot",
       center = T) +
  theme(plot.title = element_text(size=7)) + 
  theme(axis.title.y  = element_text(size = 4)) +
  theme_bw()

#output_file = "foot_Contrasts.pdf"
#ggsave(output_file, width = 9, height = 4.5)
```

#### Mass

```{r}
mass_plot <- mass_draws %>%
  filter(row_number() %% 10 == 1) %>%
  compare_levels(.value, by = .variable)  %>%
  ungroup() %>%
  mutate(condition = reorder(.variable, .value)) %>%
  ggplot(aes(y = .variable, x = .value)) + 
  geom_halfeyeh() + 
  #stat_dotsh(quantiles = 150, dotsize = 1.2) +
  geom_vline(xintercept = c(0), linetype = "dashed") +
  scale_fill_manual(values = c("gray80")) + 
  labs(x = "Relative Mass Differences\n",
       y = "",
       #title = "Mass",
       center = T) +
  theme(plot.title = element_text(size=7)) + 
  theme(axis.title.y  = element_text(size = 4)) +
  theme_bw()

#output_file = "mass_Contrasts.pdf"
#ggsave(output_file, width = 9, height = 4.5)
```
